### 2015-07-10 manuscript/defs2.tex
Updating defs2.tex

\begin{definition}
Let $r$ be an refd of length $l$ and let $S$ be a set of sequences,
each of length $l$.
\begin{itemize}
\item We say $r$ is \underline{consistent} with $S$ if $r$ is
  consistent with every sequence in $S$.
\item We say $r$ is \underline{tightly consistent} with $S$ if $r$ is
  consistent with $s$ and, for every $i$ such that $r_i=*$, there
  exists sequences $x,y \in S$ such that $x_i \neq y_i$.
\end{itemize}
That is: $r$ is tightly consistent with the set $S$ is $r$ only has
$*$ characters in those places it must.  (I thought this was going to
be necessary at one point, but am now doubting it.)

@@

\begin{definition}
Let $s$ be a fixed seed with length $l$, $f$ be a fixed integer, and $G$ be a fixed
genomic sequence.  An
\underline{Elementary Repeat Family} is a tuple $(r,S)$ where: 
\begin{enumerate}
\item $r$ is an refd such that $s$ covers $r$. 
\item $S$ is a set of genomic coordinates such that $|S| \geq f$.  Say
  that the sub-refds induced by $S$ are the substrings of $G$ starting
  at cordinates of $S$ and extended $|r|$ bases.
\item For every $i \in S$, $r$ is consistent with the string
  $G_{i:i+|r|}$.
\item Minimality condition.  Possibilities (I'm not sure which is
  right):
  \begin{itemize}
  \item There is no sub-refd $r'$ of $r$ that is covered by $s$ and is
     consistent some sequence $x$ that is sits outside the sequences
      induced by $S$.
  \item There is no $l$-mer $r'$ contained in $r$ that is consistence
    with $s$, such that $\sigma_s(r)'$ occurs anywhere in $G$ outside
    of the sequences induced by $S$.
 \end{itemize}
\item There is no refd $r'$ containing $r$ such that every sequence
  induced by $S$ is contained by some sequence consisted with $r'$.
\end{definition}

@@

Assume a fixed seed $s$ of length $l$ and a fixed genome $G4.

\begin{lemma}
Let $r$ and $r'$ be two different $l$

>>>>

\begin{definition}
Let $r$ be an refd of length $l$ and let $S$ be a set of sequences,
each of length $l$.
\begin{itemize}
\item We say $r$ is \underline{consistent} with $S$ if $r$ is
  consistent with every sequence in $S$.
\item We say $r$ is \underline{tightly consistent} with $S$ if $r$ is
  consistent with $s$ and, for every $i$ such that $r_i=*$, there
  exists sequences $x,y \in S$ such that $x_i \neq y_i$.
\end{itemize}
\end{definition}
That is: $r$ is tightly consistent with the set $S$ is $r$ only has
$*$ characters in those places it must.  (I thought this was going to
be necessary at one point, but am now doubting it.)

@@

\begin{definition}
Let $s$ be a fixed seed with length $l$, $f$ be a fixed integer, and $G$ be a fixed
genomic sequence.  An
\underline{Elementary Repeat Family} is a tuple $(r,S)$ where: 
\begin{enumerate}
\item $r$ is an refd such that $s$ covers $r$. 
\item $S$ is a set of genomic coordinates such that $|S| \geq f$.  Say
  that the sub-refds induced by $S$ are the substrings of $G$ starting
  at cordinates of $S$ and extended $|r|$ bases.
\item For every $i \in S$, $r$ is consistent with the string
  $G_{i:i+|r|}$.
\item Minimality condition.  Possibilities (I'm not sure which is
  right):
  \begin{itemize}
  \item There is no sub-refd $r'$ of $r$ that is covered by $s$ and is
     consistent some sequence $x$ that is sits outside the sequences
      induced by $S$.
  \item There is no $l$-mer $r'$ contained in $r$ that is consistence
    with $s$, such that $\sigma_s(r)'$ occurs anywhere in $G$ outside
    of the sequences induced by $S$.
 \end{itemize}
\item There is no refd $r'$ containing $r$ such that every sequence
  induced by $S$ is contained by some sequence consisted with $r'$.
\end{enumerate}
\end{definition}

@@

Assume a fixed seed $s$ of length $l$ and a fixed genome $G$.
